Supplementary materials

### 2018-07-11 WholePlotTrajectories_SuppMat.Rmd
biblio last reread

---
title: "Appendix I"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Eric MARCON
    authsuperscript: 1
  - name: Bruno HERAULT
    authsuperscript: 2
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: INPHB (Institut National Ploytechnique Félix Houphoüet Boigny) 
    address: Yamoussoukro, Ivory Coast
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: http://www.ecofog.gf/spip.php?article47
journalinfo: Hal 00679993
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings}
lang: english
output: 
  bookdown::gitbook: default
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::word_document2: default
---

@@

**Figure A1**: Whenever the family or genus were recorded for a vernacular name, the pool of species sampled to replace the vernacular name was restricted to those pertaining to the same higher taxonomic level (i.e species of the same genus when the species is missing, species of the same family when the genus is missing) \@ref(fig:FigBayesianScheme).

**Figure A2**: Scheme of the redundancy measurement process

**Figure A3**: Trajectories of seed mass classes proportions over 30 years after disturbance, corresponding to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. No gap filling process was applied in this case. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3 \@ref(fig:FigSeedMassClasses).

**Figure A4**: Trajectories of the Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.and the missing trait value filling processes. \@ref(fig:DivFun).

**Figure A5**: Summarizing plots of the functional PCA analysis defining communities functional space. **(a)** Plot of the samples from the BRIDGE functional database in the two dimensional main plan. **(b)** bow plot of the PCA eignevalues in percentage. **(c)** Plot of the 7 functional traits sed in the PCA analysis (Leaf and stem traits, and maximum species height). \@ref(fig:PCA_graphs).

**Figure A6**: Trajectories of the functional redundancy over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation and the missing trait value filling processes. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3. \@ref(fig:RedFun).

@@

# **Figure A1**: Bayesian process sheme

@@

# **Figure A2**: Redundancy metric

```{r RedMM,out.width='100%',fig.cap="Scheme of the redundancy measurement process",echo=F, fig.env="figure*"}
knitr::include_graphics("ExternalFig/RedundancyMetric.png")
```

# **Figure A3**: Proportion of seed mass classes along time

```{r FigSeedMassClasses, echo=FALSE, out.width='80%', fig.asp=2/5,fig.cap="Trajectories of seed mass classes proportions over 30 years after disturbance, corresponding to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. No gap filling process was applied in this case. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.", fig.env="figure*"}
load("DB/Smass_ClassProp")

@@

# **Figure A4**: Rao diversity trajectories with all plots display

```{r DivFun, out.width = '60%', echo=FALSE, fig.cap="Trajectories of the Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.and the missing trait value filling processes.", fig.env="figure*"}
load("DB/FunctionalTraj_ForGraphs")

FunTraj(CompleteFun,remove=F)

# **Figure A5**: Simpson and Rao Linera regrassion summary

```{r LinReg, echo=FALSE,is.as=T}
LmSummary <- data.frame(
  Diversity=c(rep("Simpson",2), rep("Rao",2)),
  Metrics=rep(c("R^2^","p~value~"),times=2),
  Time1=c("-0.08","0.7",
            "0.58","4e-3"),
  Time2=c("0.25","6e-2",
            "0.58","4e-3"),
  Time3=c("0.24","6e-2",
            "0.58","4e-3")
)
names(LmSummary) <- c("Diversity","Metrics","10 years", "20 years", "30 years")
knitr::kable(LmSummary, "html", caption="Linear models information", longtable = FALSE, booktabs = TRUE, escape = FALSE) %>%
  collapse_rows(columns=1) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = TRUE)
```

# **Figure A6**: Functional PCA

```{r PCA_graphs, out.width = '100%', echo=FALSE, fig.cap="Summarizing plots of the functional PCA analysis defining communities functional space. (ref:Bolda) Plot of the samples from the BRIDGE functional database in the two dimensional main plan. (ref:Boldb) bow plot of the PCA eignevalues in percentage. (ref:Boldc) Plot of the 7 functional traits sed in the PCA analysis (Leaf and stem traits, and maximum species height).", fig.env="figure*"}
load("DB/FunctionalPCA")

plotPCA(DataACP)

# **Figure A7**: Overall functional redundancy

```{r RedFun, out.width = '100%', echo=FALSE, fig.cap="Trajectories of the functional redundancy over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation and the missing trait value filling processes. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.", fig.env="figure*"}
load("DB/Redundancy")

par(mar=c(5,4,5,2))
RedundancyPlot(RedundancyTraj)
mtext("Functional Redundancy",side=3,adj=0,line=0.5)
mtext("Years since disturbance",side=1,line=2.2,adj=1)

>>>>

---
title: "Supplementary materials"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Eric MARCON
    authsuperscript: 1
  - name: Bruno HERAULT
    authsuperscript: 2
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: INPHB (Institut National Ploytechnique Félix Houphoüet Boigny) 
    address: Yamoussoukro, Ivory Coast
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: http://www.ecofog.gf/spip.php?article47
journalinfo: Hal 00679993
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings}
lang: english
output: 
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::gitbook: default
  bookdown::word_document2: default
---

@@

**Figure S1**: Whenever the family or genus were recorded for a vernacular name, the pool of species sampled to replace the vernacular name was restricted to those pertaining to the same higher taxonomic level (i.e species of the same genus when the species is missing, species of the same family when the genus is missing) \@ref(fig:FigBayesianScheme).

**Figure S2**: Trajectories of seed mass classes proportions over 30 years after disturbance, corresponding to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. No gap filling process was applied in this case. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3 \@ref(fig:FigSeedMassClasses).

@@

# **Figure S1**: Bayesian process sheme

@@

# **Figure S2**: Proportion of seed mass classes along time

```{r FigSeedMassClasses, echo=FALSE, out.width='80%', fig.asp=2/5,fig.cap="Trajectories of seed mass classes proportions over 30 years after disturbance. Colors are treatments: green (control), yellow (T1), orange (T2), red (T3).", fig.env="figure*"}
load("DB/Smass_ClassProp")

@@

### 2018-07-11 WholePlotTrajectories_SuppMat.tex
biblio last reread

\PaperTitle{Appendix I} % Article title

@@

\textbf{Figure A1}: Whenever the family or genus were recorded for a
vernacular name, the pool of species sampled to replace the vernacular
name was restricted to those pertaining to the same higher taxonomic
level (i.e species of the same genus when the species is missing,
species of the same family when the genus is missing)
\ref{fig:FigBayesianScheme}.

\textbf{Figure A2}: Scheme of the redundancy measurement process

\textbf{Figure A3}: Trajectories of seed mass classes proportions over
30 years after disturbance, corresponding to the median (solid line) and
0.025 and 0.975 percentile (gray envelope) observed after 50 iteration
of the taxonomic uncertainty propagation. No gap filling process was
applied in this case. Initial treatments are represented by solid lines
colors with green for control, blue for T1,orange for T2 and red for T3
\ref{fig:FigSeedMassClasses}.

\textbf{Figure A4}: Trajectories of the difference to the 1989
inventories (5 years after disturbance) over 30 years after disturbance
of plots communities \textbf{(a)} Richness, \textbf{(b)} Shannon and
\textbf{(c)} Simpson diversities. Trajectories correspond to the median
(solid line) and 0.025 and 0.975 percentile (gray envelope) observed
after 50 iteration of the taxonomic uncertainty propagation. Initial
treatments are represented by solid lines colors with green for control,
blue for T1,orange for T2 and red for T3 \ref{fig:DivTaxo}.

\textbf{Figure A5}: Trajectories of the Rao functional diversity over 30
years after disturbance. Trajectories correspond to the median (solid
line) and 0.025 and 0.975 percentile (gray envelope) observed after 50
iteration of the taxonomic uncertainty propagation. Initial treatments
are represented by solid lines colorswith green for control, blue for
T1,orange for T2 and red for T3.and the missing trait value filling
processes. \ref{fig:DivFun}.

\textbf{Figure A6}: Summarizing plots of the functional PCA analysis
defining communities functional space. \textbf{(a)} Plot of the samples
from the BRIDGE functional database in the two dimensional main plan.
\textbf{(b)} bow plot of the PCA eignevalues in percentage. \textbf{(c)}
Plot of the 7 functional traits sed in the PCA analysis (Leaf and stem
traits, and maximum species height). @ref(fig:PCA\_graphs).

\textbf{Figure A7}: Trajectories of the functional redundancy over 30
years after disturbance. Trajectories correspond to the median (solid
line) and 0.025 and 0.975 percentile (gray envelope) observed after 50
iteration of the taxonomic uncertainty propagation and the missing trait
value filling processes. Initial treatments are represented by solid
lines colors with green for control, blue for T1,orange for T2 and red
for T3. \ref{fig:RedFun}.

@@

\section{\texorpdfstring{\textbf{Figure A1}: Bayesian process
sheme}{Figure A1: Bayesian process sheme}}\label{figure-a1-bayesian-process-sheme}

@@

\section{\texorpdfstring{\textbf{Figure A2}: Redundancy
metric}{Figure A2: Redundancy metric}}\label{figure-a2-redundancy-metric}

@@

\section{\texorpdfstring{\textbf{Figure A3}: Proportion of seed mass
classes along
time}{Figure A3: Proportion of seed mass classes along time}}\label{figure-a3-proportion-of-seed-mass-classes-along-time}

@@

{\centering \includegraphics[width=0.8\linewidth]{AppendixI_files/figure-latex/FigSeedMassClasses-1}

@@

\caption{Trajectories of seed mass classes proportions over 30 years after disturbance, corresponding to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. No gap filling process was applied in this case. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.}\label{fig:FigSeedMassClasses}
\end{figure*}

\section{\texorpdfstring{\textbf{Figure A4}: Richness, Shannon and
Simpson taxonomic diversity
trajectories}{Figure A4: Richness, Shannon and Simpson taxonomic diversity trajectories}}\label{figure-a4-richness-shannon-and-simpson-taxonomic-diversity-trajectories}

{\centering \includegraphics[width=1\linewidth]{AppendixI_files/figure-latex/DivTaxo-1}

\caption{Trajectories of the difference to the 1989 inventories (5 years after disturbance) over 30 years after disturbance of plots communities \textbf{(a)} Richness, \textbf{(b)} Shannon and \textbf{(c)} Simpson diversities. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.}\label{fig:DivTaxo}
\end{figure*}

\section{\texorpdfstring{\textbf{Figure A5}: Rao diversity trajectories
with all plots
display}{Figure A5: Rao diversity trajectories with all plots display}}\label{figure-a5-rao-diversity-trajectories-with-all-plots-display}

{\centering \includegraphics[width=0.6\linewidth]{AppendixI_files/figure-latex/DivFun-1}

\caption{Trajectories of the Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.and the missing trait value filling processes.}\label{fig:DivFun}
\end{figure*}

\section{\texorpdfstring{\textbf{Figure A6}: Functional
PCA}{Figure A6: Functional PCA}}\label{figure-a6-functional-pca}

{\centering \includegraphics[width=1\linewidth]{AppendixI_files/figure-latex/PCA_graphs-1}

\caption{Summarizing plots of the functional PCA analysis defining communities functional space. \textbf{(a)} Plot of the samples from the BRIDGE functional database in the two dimensional main plan. \textbf{(b)} bow plot of the PCA eignevalues in percentage. \textbf{(c)} Plot of the 7 functional traits sed in the PCA analysis (Leaf and stem traits, and maximum species height).}(\#fig:PCA_graphs)
\end{figure*}

\section{\texorpdfstring{\textbf{Figure A7}: Overall functional
redundancy}{Figure A7: Overall functional redundancy}}\label{figure-a7-overall-functional-redundancy}

{\centering \includegraphics[width=1\linewidth]{AppendixI_files/figure-latex/RedFun-1}

\caption{Trajectories of the functional redundancy over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation and the missing trait value filling processes. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.}\label{fig:RedFun}
\end{figure*}

>>>>

\PaperTitle{Supplementary materials} % Article title

@@

\textbf{Figure S1}: Whenever the family or genus were recorded for a
vernacular name, the pool of species sampled to replace the vernacular
name was restricted to those pertaining to the same higher taxonomic
level (i.e species of the same genus when the species is missing,
species of the same family when the genus is missing)
\ref{fig:FigBayesianScheme}.

\textbf{Figure S2}: Scheme of the redundancy measurement process

\textbf{Figure S3}: Trajectories of seed mass classes proportions over
30 years after disturbance, corresponding to the median (solid line) and
0.025 and 0.975 percentile (gray envelope) observed after 50 iteration
of the taxonomic uncertainty propagation. No gap filling process was
applied in this case. Initial treatments are represented by solid lines
colors with green for control, blue for T1,orange for T2 and red for T3
\ref{fig:FigSeedMassClasses}.

@@

\section{\texorpdfstring{\textbf{Figure S1}: Bayesian process
sheme}{Figure S1: Bayesian process sheme}}\label{figure-s1-bayesian-process-sheme}

@@

\section{\texorpdfstring{\textbf{Figure S2}: Redundancy
metric}{Figure S2: Redundancy metric}}\label{figure-s2-redundancy-metric}

@@

\section{\texorpdfstring{\textbf{Figure S3}: Proportion of seed mass
classes along
time}{Figure S3: Proportion of seed mass classes along time}}\label{figure-s3-proportion-of-seed-mass-classes-along-time}

@@

{\centering \includegraphics[width=0.8\linewidth]{WholePlotTrajectories_SuppMat_files/figure-latex/FigSeedMassClasses-1}

@@

\caption{Trajectories of seed mass classes proportions over 30 years after disturbance. Colors are treatments: green (control), yellow (T1), orange (T2), red (T3).}\label{fig:FigSeedMassClasses}
\end{figure*}
